### 2020-07-19 article.tex
minor

% REQUIRED
\begin{abstract}
  Contemporary applications in computational science and engineering often
    require the solution of linear systems which may be of different sizes,
    shapes, and structures. The goal of this paper is to explain how two
    libraries, PETSc and HPDDM, have been interfaced together in order to offer
    end-users robust overlapping Schwarz preconditioners and advanced Krylov
    methods featuring recycling and block solution techniques.
    The flexibility of the implementation %, which for example may deal with various matrix formats,
    is showcased and explained with minimalist, easy-to-run, and reproducible examples,
    to ease the integration of these algorithms into more advanced frameworks.
    The examples simulate the linear or nonlinear solves of typical
    applications in fracture mechanics, linear stability analysis or more
    broadly-speaking eigenanalysis, elasticity, combustion, and
    electromagnetism.
\end{abstract}

@@

\subsubsection{Blocking inside SLEPc\label{sec:lobpcg}}
The implementations of the Locally Optimal Block Preconditioned Conjugate
Gradient~\cite{knyazev2001toward}~(LOBPCG) and the Contour Integral Spectrum
Slicing method~\cite{sakurai2003projection}~(CISS) in SLEPc were previously not
using blocking when applying the preconditioner or solving linear systems. In
version 3.14.0, these solvers have been adapted to employ \pk{KSPMatSolve} and
\pk{PCMatApply}.  In the case of LOBPCG, which is a purely blocked method, all
steps were already implemented as block operations, except the applications of
the preconditioner, which undermined the benefits of blocking. With the new
implementation, the gains are striking, as reported in~\cref{sec:lobpcg}.

Finally, the performance of LOBPCG~\cite{knyazev2001toward} as implemented in SLEPc is studied using three different preconditioners:

@@

In this paper, we presente the interface between PETSc and HPDDM. The new
registered Krylov and overlapping Schwarz methods are explained and we show the
applicability of these  with numerical examples. Solving well-known problems,
we describe various runtime options. %Some more unconventional test
%cases were commented as well, for example using \pk{MatKAIJ} or \pk{MatIS} matrix types.
Overall, the interface paves the way for having recycling and block Krylov
methods plus robust overlapping Schwarz methods using the GenEO framework in
PETSc.

>>>>

% REQUIRED
\begin{abstract}
  Contemporary applications in computational science and engineering often
    require the solution of linear systems which may be of different sizes,
    shapes, and structures. The goal of this paper is to explain how two
    libraries, PETSc and HPDDM, have been interfaced together in order to offer
    end-users robust overlapping Schwarz preconditioners and advanced Krylov
    methods featuring recycling and block solution techniques.
    The flexibility of the implementation %, which for example may deal with various matrix formats,
    is showcased and explained with minimalist, easy-to-run, and reproducible examples,
    to ease the integration of these algorithms into more advanced frameworks.
    The examples provided cover applications from
    %simulate the linear or nonlinear solves of typical
    %applications in fracture mechanics, linear stability analysis or more
    %broadly-speaking
    eigenanalysis, elasticity, combustion, and
    electromagnetism.
\end{abstract}

@@

\subsubsection{Blocking inside SLEPc\label{sec:lobpcg}}
The implementations of the Locally Optimal Block Preconditioned Conjugate
Gradient~\cite{knyazev2001toward}~(LOBPCG) and the Contour Integral Spectrum
Slicing method~\cite{sakurai2003projection}~(CISS) in SLEPc were previously not
using blocking when applying the preconditioner or solving linear systems. In
version 3.14.0, these solvers have been adapted to employ \pk{KSPMatSolve} and
\pk{PCMatApply}.  In the case of LOBPCG, which is a purely blocked method, all
steps were already implemented as block operations, except the applications of
the preconditioner, which undermined the benefits of blocking.
%With the new
%implementation, the gains are striking, as reported in~\cref{sec:lobpcg}.

The performance of LOBPCG~\cite{knyazev2001toward} as implemented in SLEPc is studied using three different preconditioners:

@@

In this paper, we presented the interface between PETSc and HPDDM and discussed the new Krylov and overlapping Schwarz methods, providing several
numerical examples and describing various runtime options. %Some more unconventional test
%cases were commented as well, for example using \pk{MatKAIJ} or \pk{MatIS} matrix types.
Overall, the interface paves the way for having recycling and block Krylov
methods plus robust overlapping Schwarz methods using the GenEO framework in
PETSc.
